---
title: "Project"
author: "Xuechen Yan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

My project is calculate two risk measure: VaR and CVaR.

#Project 1

VaR (value at risk) literally means "value at risk", which means the maximum possible loss of a financial asset or portfolio under normal market fluctuation. More precisely, it refers to the maximum possible loss of the value of a financial asset or portfolio in a specific future period under a certain probability level (confidence level).

The expression of VaR is:

$$
V a R_{\alpha}=\min \{x \in R: P\{X \leq x\} \geq \alpha\}
$$
where $X$ is random simple of loss.

```{r}
VaR=function(X,alpha){
  VaR=quantile(X,1-alpha)
  return(VaR)
}
X=rnorm(1e3,5e-4,1e-3)
alpha=.05
VaR=VaR(X,alpha)
print(list('VaR'=VaR))
```


#Project 2

## Conditional Value-at-Risk 

Let $Z$ be a bounded-mean random variable, i.e., $\mathbb{E}[|Z|]<\infty,$ on a probability space $(\Omega, \mathcal{F}, \mathbb{P})$, with cumulative distribution function $F(z)=\mathbb{P}(Z \leq z) .$ In this paper we interpret $Z$ as a cost. The value-at-risk (VaR) at confidence level $\alpha \in(0,1)$ is the $1-\alpha$ quantile of $Z,$ i.e., $\operatorname{VaR}_{\alpha}(Z)=$ $\min \{z \mid F(z) \geq 1-\alpha\} .$ The conditional value-at-risk (CVaR) at confidence level $\alpha \in(0,1)$ is defined as [20] :
$$
\operatorname{CVaR}_{\alpha}(Z)=\min _{w \in \mathbb{R}}\left\{w+\frac{1}{\alpha} \mathbb{E}\left[(Z-w)^{+}\right]\right\}
$$
where $(x)^{+}=\max (x, 0)$ represents the positive part of $x$. 

$\operatorname{CVaR}_{\alpha}(Z)$ may be interpreted as the expected value of $Z$, conditioned on the $\alpha$ -portion of the tail distribution. It is well known that $\mathrm{CVaR}_{\alpha}(Z)$ is decreasing in $\alpha, \mathrm{CVaR}_{1}(Z)$ equals to $\mathbb{E}(Z),$ and $\mathrm{CVaR}_{\alpha}(Z)$ tends to $\max (Z)$ as $\alpha \downarrow 0 .$ During the last decade, the CVaR risk-measure has gained popularity in financial applications, among others. 

```{r}
positive.mean=function(X,x){
  n=length(X)
  a=numeric(n)
  for (i in 1:n) {
    if(X[i]-x>=0)
      a[i]=X[i]-x
    else
      a[i]=0
  }
  return(mean(a))
}

CVaR=function(X,alpha){
  f=function(x)
    x+1/(1-alpha)*positive.mean(X,x)
  CVaR=optimize(f,lower = quantile(X,1-alpha),upper = max(X))
  return(CVaR)
}
X=rnorm(1e3,5e-4,1e-3)
alpha=.05
CVaR=CVaR(X,alpha)
print(list("CVaR"=CVaR$objective))
```

